---
title: "HW3"
author: "Tianhui He"
date: "2019/10/11"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(ggplot2)
library(ggridges)
library(tidyverse)
```

###Problem 1
Basic setup:
```{r}
library(p8105.datasets)
data("instacart")
```
The dataset instacart has dimention of 1384617 X 15. Variables include order_id, product_id, add_to_cart_order, reordered, user_id, eval_set, order_number, order_dow, order_hour_of_day, days_since_prior_order, product_name, aisle_id, department_id, aisle, department. Important characters include product_name and aisle while some viatal numeric variables are product_id and order_hour_of_day. Important varibles used to solve this question include product_name since this is a unique identifier of products, and manipulation involve products is based on this important variable.
```{r}
ins_aisles = 
instacart %>%
  count(aisle, name ="number_aisles") %>%
  arrange(desc(number_aisles)) 
```
By using the count command, we can see that fresh vegetables is the most item ordered from. There are 134 aisles(also use length function to check) and the number of fresh vegetables is 150609.

Scatterplot:
```{r}
ins_aisles%>%
  filter(number_aisles > 10000) %>%
  ggplot(aes(y = aisle, x = number_aisles)) + 
  geom_point(alpha = .5)
```
Here, I use a scatterplot rather a histogram,because it shows a more clear graph of relative position among the count of each kind of aisle.
```{r}
instacart_pop =
instacart %>%
  group_by(aisle) %>%
  count(product_name, name ="number_product_name") %>%
  filter(aisle %in% c("baking ingredients", "dog food care", "packaged vegetables fruits")) 
instacart_pop %>% 
  group_by(aisle) %>% 
  arrange(desc(number_product_name)) %>% 
  top_n(3) %>% 
  knitr :: kable()
  
```

A table shows the mean of hour:
```{r}
instacart_mean =
  instacart %>% 
  drop_na() %>% 
  distinct() %>% 
  select(product_name,order_dow,order_hour_of_day) %>% 
  filter(product_name %in% c("Pink Lady Apples","Coffee Ice Cream")) 
instacart_mean =
  instacart_mean %>% 
   mutate(
  order_dow = recode(order_dow, '0' = "Sunday",'1' = "Monday",'2' = "Tuesday",'3' = "Wednesday", '4' = "Thursday", '5' =    "Friday", '6' = "Saturday")
 ) %>% 
  group_by(order_dow, product_name) %>% 
  summarize(
    mean_order_hour_of_day = mean(order_hour_of_day)) %>%
  pivot_wider(names_from = order_dow,
              values_from = mean_order_hour_of_day) %>% 
  select(product_name, Sunday, Monday, Tuesday, Wednesday, Thursday, Friday, Saturday)
knitr :: kable(instacart_mean)
```


### Problem 2
Basic data cleaning:
```{r}
library(p8105.datasets)
data("brfss_smart2010") 
brfss = 
  brfss_smart2010 %>% 
  janitor::clean_names() %>%  #format the data use appropriate variable names
  filter(topic == "Overall Health") %>% #focus on topic
  filter(response %in% c("Excellent","Very good","Good","Fair","Poor")) %>%  # responses from "Excellent" to "Poor", used unique command to check what are categories in response
  mutate(
     response = as.factor(response),
     response = fct_relevel(response, c("Poor","Fair","Good","Very good","Excellent"))) %>%   
     arrange(response,desc(response))#responses as a factor taking levels orders
```
For 2002, there are six states were observed at 7 or more locations. They were CT, FL, MA, NC, NJ,and PA.
```{r}
brfss_2002= 
  brfss %>%
  select(year,locationabbr,locationdesc) %>% 
  filter(year == "2002") %>% 
  group_by(locationabbr) %>% 
  count(locationabbr, name = "number_of_location") %>% 
  mutate(
    number_of_location = number_of_location/5
  ) %>% 
  filter(number_of_location > 6)
brfss_2002

```
For 2010, there is a significant increase in the number of locations that satisfy our requirements. Specifically, 14 states are obseved at 7 or more locations.
```{r}
brfss_2010= 
  brfss %>%
  select(year,locationabbr,locationdesc) %>% 
  filter(year == "2010") %>% 
  group_by(locationabbr) %>% 
  count(locationabbr, name = "number_of_location") %>% 
  mutate(
    number_of_location = number_of_location/5
  ) %>% 
  filter(number_of_location > 6)
brfss_2010
```
```{r}
brfss_datavalue = 
brfss %>% 
  filter(response == "Excellent") %>% 
  group_by(locationabbr, year) %>% 
  summarize(
    mean_data_value = mean(data_value),
    ) %>% 
  drop_na()
brfss_datavalue
```

A "spaghetti" plot:
```{r}
ggplot(brfss_datavalue, aes(x = year, y = mean_data_value, color = locationabbr)) + 
  geom_line()
```
A two panel plot for 2006 and 2010:
```{r}
library(patchwork)
Two = 
brfss %>% 
  filter(year %in%  c("2006","2010")) %>% 
  select(year,locationabbr,response, data_value,locationdesc) %>% 
  drop_na() %>% 
  filter(response %in% c("Excellent","Very good","Good","Fair","Poor")) %>% 
  filter(locationabbr == "NY")

Two %>% 
  group_by(year,locationdesc,locationabbr) %>% 
  ggplot(aes(x = response, y = data_value, fill = locationdesc)) + 
  geom_bar(stat = "identity", position = "dodge") +
  facet_grid(year ~ .) +
  labs(
    title = "Distribution for Responses among locations in NY",
    x = "Response",
    y = "Count of Data Value"
  )
```
This graoh has an emphases on different locations among New York States. I did another graph only showing the distribution across New York City. This one utilizes a violin plot. I think here, geom_violin gives a better idea of how distribution looks than boxplot does.

```{r}
Two %>% 
  group_by(year,locationdesc,locationabbr) %>% 
  ggplot(aes(x = response, y = data_value)) + 
  geom_violin() +
  facet_grid(year ~ locationabbr) +
  labs(
    title = "Distribution for Responses in NY",
    x = "Response",
    y = "Count of Data Value"
  )
```
### Problem 3
Because the original data frame is not shown in a data frame that is easy to manipulate. So I use pivot longer to change the data format. Initually, it has 1443 columns and now I transpose variable activity numbers into observation numbers. The new table contains 6 variables and 50400 observations.The new variable "WeekDay" I creat is to point out whether that day is a weekday. Important vairables include week(int), day_id(int), activity_number(char), day(char) and activity_counts(dbl) and WeekDay(char). Since the table is already tailored into a more concise one, I think each variable is as important as each other :)
```{r}
accel= read_csv("accel_data.csv") %>% 
  janitor::clean_names() %>% 
  pivot_longer(
    activity_1:activity_1440,
    names_to = "activity_number",
    values_to = "activity_counts"
  ) %>% 
mutate(
  WeekDay = ifelse(day == "Saturday" | day == "Sunday", "weekend", "weekday")
) %>% #new variable indicate weekday or weekend day
  mutate(
  activity_number = factor(activity_number)) # change activity number as a factor

  knitr::kable(head(accel,30)) # this is such a long table, so showing just the first 30 rows

```

My table for this question has 35 observation, containning 7 observations for each day. There's an increasing trend in the number of activity from Monday to Friday, except for weeks 3 and 4. In general, sunday has a low number of activities compared across other weekdays within the same week.
```{r}
accel_day = 
accel %>% 
  group_by(week,day) %>%
  mutate(
    sum_activity_day = sum(activity_counts)
    ) %>% 
  select(week, day_id, day, sum_activity_day) %>% 
  distinct()
  knitr::kable(accel_day)
```
A plot:
```{r}
accel %>% mutate(
  activity_number = factor(substr(activity_number,10,13), ordered = TRUE, levels = c(1:1440))
  ) %>% 
  ggplot(aes(x = factor(activity_number), y = activity_counts, fill = day)) +
  scale_x_discrete(breaks = seq(60, 1440, by=60),labels = as.character(c(1:24))) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(
    title = "Inspection Activity over Day",
    x = "Week",
    y = "Count of Activity per Day"
  )
```

In this plot, I use hour as the plotting unit. So we can see a activity distribution across hours in everyday. In general, we can see that the patient's activity peak is between 18:00 to 21:00, and there is one extremely high peak happened during this time period which is over 10,000. On the other hand, we can see that the patient has fewer activity during 0 to 5. By rationality, this indicates that this patient is sleeping and that's why he conducts much fewer activities.   